---
title: "Appendix: R Code - Group 3 Final Project"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval=FALSE)

# load requisite packages
library(dplyr)
library(haven)
library(ordinal)
library(tidyr)
library(kableExtra)
library(magick)
library(ggplot2)

def.par <- par(no.readonly = TRUE)
```

# DATA PREP
```{r UK survey data}
# Load interviewer data
ESS5INT<-read_por("ESS5INTe03sas.por")

# Subset Great Britain (GB) data and select interviewer ID (INTNUM), gender (INTGNDR), age (INTAGEA), and R's ID (IDNO) 
UKint <- ESS5INT %>% 
  mutate(intid=as.numeric(ESS5INT$INTNUM), 
    gender=factor(ESS5INT$INTGNDR), 
    age=as.numeric(INTAGEA), 
    respondent=as.character(ESS5INT$IDNO)) %>%
  subset(CNTRY=="GB") %>% 
  select(intid, gender, age, respondent)

# Read in survey data
ESS5<-read_sas("ess5e03_4.sas7bdat")

# reformat IDs
ESS5$idno<-as.numeric(ESS5$idno) # convert respondent IDs to numeric in respondent data
UKint$respondent<-as.numeric(UKint$respondent) # convert respondent IDs to numeric in interviewer data

# Join interviewer characteristics, respondent characteristics, the four outcomes of interest, and weights.
UK_data <- UKint %>%
  left_join(ESS5, by = c("respondent" = "idno")) %>%
  select(intid, gender, age, region, respondent, happy, freehms, tvtot, pray, gndr, agea, domicil, pspwght)

# recode missing data
UK_data$age[UK_data$age==999]<-NA # NA interviewer with age coded as 999
UK_data$agea[UK_data$agea==999]<-NA # NA respondents with agea coded as 999
UK_data$gndr[UK_data$gndr==9]<-NA # NA for respondent with gndr coded as 9
UK_data$happy[UK_data$happy==77]<-NA # convert 1 refusal to NA
UK_data$happy[UK_data$happy==88]<-NA # convert 3 don't know's to NA
UK_data$freehms[UK_data$freehms==8]<-NA # convert 37 don't know's to NA
UK_data$tvtot[UK_data$tvtot==88]<-NA # convert 4 don't know's to NA
UK_data$pray[UK_data$pray==88]<-NA # convert 15 don't know's to NA
UK_data$pray[UK_data$pray==77]<-NA # convert 3 refusals to NA
UK_data$domicil[UK_data$domicil==8]<-NA # convert 9 no answer to NA

# Mutate UK data for modeling
UK_data<-UK_data %>%
  mutate(intid = intid,
    intgndr = factor(ifelse(gender==1, 0, 1), levels = c(0,1), labels = c("Male", "Female")),
    intage = age,
    intagec = age-55.76587,
    rid = respondent,
    region = factor(ifelse(region=="UKC", "01.NE-England", 
       ifelse(region=="UKD", "02.NW-England",
         ifelse(region=="UKE", "03.Yorkshire",
           ifelse(region=="UKF", "04.East Midlands",
             ifelse(region=="UKG", "05.West Midlands",
          ifelse(region=="UKH", "06.East of England",
            ifelse(region=="UKI", "07.London",
              ifelse(region=="UKJ", "08.SE-England",
                ifelse(region=="UKK", "09.SW-England",
                  ifelse(region=="UKL", "10.Wales", 
                    ifelse(region=="UKM", "11.Scotland", "12.NorthernIE")))))))))))),
    domicil = factor(ifelse(domicil<3, 1, ifelse(domicil==3, 2, 3)), levels = c(1:3), labels = c("HighPop", "MedPop", "LowPop")),
    rgndr = factor(ifelse(gndr==1, 0, 1), levels = c(0,1), labels = c("Male", "Female")),
    rage = agea,
    ragec = agea-49.83394,
    happy = factor(ifelse(happy<5, -1, ifelse(happy>5, 1, 0)), levels = c(-1, 0, 1), labels = c("Unhappy", "Neutral", "Happy"), ordered=TRUE),
    freehms = factor(freehms, levels=c(1,2,3,4,5), labels = c("Agree Strongly", "Agree", "Neutral", "Disagree", "Disagree Strongly"),ordered=TRUE), 
    tvtot = factor(tvtot, levels=c(0,1,2,3,4,5,6,7), labels = c("0 min", "<30 min", "30-60 min", "61-90 min", "91-120 min", "121-150 min", "151-180 min", ">180 min"), ordered=TRUE),
    pray = factor(pray, levels = c(1:7), labels = c("Daily", ">1 Weekly", "Weekly", ">=1 Monthly", "Holy Days", "Less Often", "Never"), ordered = TRUE),
    pspwght = pspwght, .keep = "none")

# subset case.complete data to interviewers who fully completed five or more interviews & add total interviews
UKfiveplus<-UK_data[complete.cases(UK_data),] %>%
  group_by(intid) %>%
  filter(n()>4) %>%
  mutate(totalints = n_distinct(rid))

# clean up environment
rm(list = c("ESS5", "ESS5INT", "UKint"))

save(UK_data, file="UK_withNA_data_final.RData")
save(UKfiveplus, file="UK_clean_data_final.RData")
```

# DATA SUMMARIES
## Interview Summary
```{r}
# number of unique interviewers
n_distinct(UKfiveplus$intid)

# mean number of interviews per interviewer
round(mean(UKfiveplus$totalints[!duplicated(UKfiveplus$intid)]), 2)

# 14 interviewers with more than one region.
UKfiveplus %>%
  group_by(intid) %>%
  summarise(multirgn = sum(n_distinct(region)>1)) 

# Interviews by interviewer.
IntsByInt<-UKfiveplus %>%
  group_by(intid) %>%
  summarise(TotalInts = sum(n_distinct(rid)),
            Male.Int = n_distinct(intid[intgndr=="Male"]),
            Female.Int = n_distinct(intid[intgndr=="Female"]))

round((sum(IntsByInt$Male.Int)/158)*100, 2)
round((sum(IntsByInt$Female.Int)/158)*100, 2)

summary(UKfiveplus$rage)

# INTERVIEWS BY DOMICIL BY REGIONS
UKfiveplus %>%
  group_by(region, domicil) %>%
  summarise(numinterviews = n_distinct(rid)) 

# summarise interviewers and interviewees by gender and region (Table 2)
Table1<-UKfiveplus %>%
  group_by(region) %>%
  summarise(N.Interviews = n_distinct(rid),
            PrcLDensity = round(sum(domicil=="LowPop")/n_distinct(rid)*100, 2),
            PrcMDensity = round(sum(domicil=="MedPop")/n_distinct(rid)*100, 2),
            PrcHDensity = round(sum(domicil=="HighPop")/n_distinct(rid)*100, 2),
            Male.Int = n_distinct(intid[intgndr=="Male"]),
            Female.Int = n_distinct(intid[intgndr=="Female"]),
            AvgAge.Int = round(mean(intage[!duplicated(UKfiveplus$intid)], na.rm = TRUE), 0),
            Male.R = sum(rgndr=="Male"),
            Female.R = sum(rgndr=="Female"),
            AvgAge.R = round(mean(rage))) 

tableNames<- c("Region", "Total <br/>Interviews", "% Low", "% Med", "% High", "Males", "Females", "Mean Age", "Males", "Females", "Mean Age" )

kable(Table1, 
      caption = "Table 1: Summary by Region", 
      booktabs = T,
      "html", 
      col.names = tableNames, # "tableNames" object created with list of names above <br/> works with "escape = FALSE" to create new line in text.
      align='lcccccccccc', # 1 character per column in table; i.e., 1 "l" for left and 10 "c" for center
      escape = FALSE) %>%
  kable_styling(latex_options = c("striped")) %>%
  add_header_above(c(" " = 2, "Population Density" = 3, "Interviewers" = 3, "Respondents" = 3)) %>% # integer indicates number of columns to be covered by 2nd level header
  save_kable("Table1.jpg")

```



## happy
```{r}
# Table of happy responses
table(UKfiveplus$happy, useNA = 'always')

# Histogram of happy responses
hist(as.numeric(UKfiveplus$happy), 
     main="Taking all things together, how happy would you say you are?", 
     xlab="Categories: 1-3 \nUnhappy - Neutral - Happy",
     ylim = c(0, 2000),
     breaks = c(0:3),
     include.lowest = T,
     xaxt="n"); axis(side=1, at=c(0, 1, 2, 3))

# table of freehms responses
table(UKfiveplus$region, UKfiveplus$happy)

# plot responses across regions
crosstabhappy<-as.data.frame(table(UKfiveplus$region, UKfiveplus$happy))
colnames(crosstabhappy)<-c("region", "category", "frequency")
ggplot(crosstabhappy, aes(x = region, y = frequency, fill = category, label = frequency)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle=60, hjust = 1)) +
  ggtitle("Taking all things together, how happy would you say you are?") +
  labs(x="Region", y="Response Frequency") +
  scale_fill_brewer(palette = "RdBu", name = "Response \nOptions")

# Box plots for happy by interviewer IDs
# par(mfrow=c(2,2))
# plot(as.numeric(UKfiveplus[UKfiveplus$intid < 2690,]$happy) ~ factor(UKfiveplus[UKfiveplus$intid < 2690,]$intid))
# plot(as.numeric(UKfiveplus[UKfiveplus$intid >= 2690 & UKfiveplus$intid < 9007,]$happy) ~ factor(UKfiveplus[UKfiveplus$intid >= 2690 & UKfiveplus$intid < 9007,]$intid)) 
# plot(as.numeric(UKfiveplus[UKfiveplus$intid >= 9007 & UKfiveplus$intid < 14388,]$happy) ~ factor(UKfiveplus[UKfiveplus$intid >= 9007 & UKfiveplus$intid < 14388,]$intid)) 
# plot(as.numeric(UKfiveplus[UKfiveplus$intid >= 14388,]$happy) ~ factor(UKfiveplus[UKfiveplus$intid >= 14388,]$intid)) 
```

## freehms
```{r}
# Table of freehms responses
table(UKfiveplus$freehms, useNA = 'always')

# Histogram of freehms responses
hist(as.numeric(UKfiveplus$freehms),
     main="Gay men and lesbians should be free to live their own life as they wish. \nTo what extent do you agree?", 
     xlab="Categories: 1-5 \nAgree Strongly - Agree - Neutral - Disagree - Dissagree Strongly", 
     breaks = c(0:5), 
     include.lowest = T,
     cex.axis=0.9) 

# table of freehms responses
table(UKfiveplus$region, UKfiveplus$freehms)

# plot responses across regions
crosstabfreehms<-as.data.frame(table(UKfiveplus$region, UKfiveplus$freehms))
colnames(crosstabfreehms)<-c("region", "category", "frequency")
ggplot(crosstabfreehms, aes(x = region, y = frequency, fill = category, label = frequency)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle=60, hjust = 1)) +
  ggtitle("Gay men and lesbians should be free to live their own life as they wish. \nTo what extent do you agree?") +
  labs(x="Region", y="Response Frequency") +
  scale_fill_brewer(palette = "RdBu", name = "Response \nOptions")

# box plots for freehms by interviewer ID-
# par(mfrow=c(2,2))
# plot(as.numeric(UKfiveplus[UKfiveplus$intid < 2690,]$freehms) ~ factor(UKfiveplus[UKfiveplus$intid < 2690,]$intid))
# plot(as.numeric(UKfiveplus[UKfiveplus$intid >= 2690 & UKfiveplus$intid < 9007,]$freehms) ~ factor(UKfiveplus[UKfiveplus$intid >= 2690 & UKfiveplus$intid < 9007,]$intid)) 
# plot(as.numeric(UKfiveplus[UKfiveplus$intid >= 9007 & UKfiveplus$intid < 14388,]$freehms) ~ factor(UKfiveplus[UKfiveplus$intid >= 9007 & UKfiveplus$intid < 14388,]$intid)) 
# plot(as.numeric(UKfiveplus[UKfiveplus$intid >= 14388,]$freehms) ~ factor(UKfiveplus[UKfiveplus$intid >= 14388,]$intid)) 
```

## tvtot
```{r}
# Table of tvtot responses
table(UKfiveplus$tvtot, useNA = 'always')

# Histogram of tvtot responses
hist(as.numeric(UKfiveplus$tvtot),
     main="On an average weekday, how much time do you spend watching TV?", 
     xlab="Categories: 1-8 \n 0.0 hrs. - 3.0+ hrs (in 0.5 hr increments)", 
     breaks = c(0:8), 
     include.lowest = T,
     xaxt="n"); axis(side=1, at=c(0,1,2,3,4,5,6,7,8))

# table of freehms responses
table(UKfiveplus$region, UKfiveplus$tvtot)

# plot responses across regions
crosstabtvtot<-as.data.frame(table(UKfiveplus$region, UKfiveplus$tvtot))
colnames(crosstabtvtot)<-c("region", "category", "frequency")
ggplot(crosstabtvtot, aes(x = region, y = frequency, fill = category, label = frequency)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle=60, hjust = 1)) +
  ggtitle("On an average weekday, how much time do you spend watching television?") +
  labs(x="Region", y="Response Frequency") +
  scale_fill_brewer(palette = "RdBu", name = "Response \nOptions")

# Box plots for tvtot by interviewer IDs
# par(mfrow=c(2,2))
# plot(as.numeric(UKfiveplus[UKfiveplus$intid < 2690,]$tvtot) ~ factor(UKfiveplus[UKfiveplus$intid < 2690,]$intid))
# plot(as.numeric(UKfiveplus[UKfiveplus$intid >= 2690 & UKfiveplus$intid < 9007,]$tvtot) ~ factor(UKfiveplus[UKfiveplus$intid >= 2690 & UKfiveplus$intid < 9007,]$intid)) 
# plot(as.numeric(UKfiveplus[UKfiveplus$intid >= 9007 & UKfiveplus$intid < 14388,]$tvtot) ~ factor(UKfiveplus[UKfiveplus$intid >= 9007 & UKfiveplus$intid < 14388,]$intid)) 
# plot(as.numeric(UKfiveplus[UKfiveplus$intid >= 14388,]$tvtot) ~ factor(UKfiveplus[UKfiveplus$intid >= 14388,]$intid))
```

## pray
```{r}
# Table of pray responses
table(UKfiveplus$pray, useNA = 'always') 

# Histogram of pray responses
hist(as.numeric(UKfiveplus$pray), 
     main="Apart from when you are at religious services, how often do you pray?", 
     xlab="Categories: 1-7 \nDaily - More than Weekly - Weekly - At Least Monthly - Holy Days - Less Often - Never",
     breaks = c(0:7), 
     ylim = c(0, 1200),
     include.lowest = T,
     cex.axis=0.9) 

# table of freehms responses
table(UKfiveplus$region, UKfiveplus$pray)

# plot responses across regions
crosstabpray<-as.data.frame(table(UKfiveplus$region, UKfiveplus$pray))
colnames(crosstabpray)<-c("region", "category", "frequency")
ggplot(crosstabpray, aes(x = region, y = frequency, fill = category, label = frequency)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle=60, hjust = 1)) +
  ggtitle("Apart from when you are at religious services, how often, if at all, do you pray?") +
  labs(x="Region", y="Response Frequency") +
  scale_fill_brewer(palette = "RdBu", name = "Response \nOptions")

# Box plots for pray by interviewer IDs
# par(mfrow=c(2,2))
# plot(as.numeric(UKfiveplus[UKfiveplus$intid < 2690,]$pray) ~ factor(UKfiveplus[UKfiveplus$intid < 2690,]$intid))
# plot(as.numeric(UKfiveplus[UKfiveplus$intid >= 2690 & UKfiveplus$intid < 9007,]$pray) ~ factor(UKfiveplus[UKfiveplus$intid >= 2690 & UKfiveplus$intid < 9007,]$intid)) 
# plot(as.numeric(UKfiveplus[UKfiveplus$intid >= 9007 & UKfiveplus$intid < 14388,]$pray) ~ factor(UKfiveplus[UKfiveplus$intid >= 9007 & UKfiveplus$intid < 14388,]$intid)) 
# plot(as.numeric(UKfiveplus[UKfiveplus$intid >= 14388,]$pray) ~ factor(UKfiveplus[UKfiveplus$intid >= 14388,]$intid))
# 
# par(def.par)
```

# HAPPY
## happy1 ~ ragec + as.factor(rgndr) + as.factor(domicil) + as.factor(region) + intagec + intgndr + (1 | intid)
```{r happy1}
# Fixed Effects only model to test against random intercept model
noint_happy1 <- clm(happy ~ ragec + rgndr + domicil + region + intagec + intgndr,
       weights = pspwght,
       Hess = TRUE,
       na.action = "na.omit",
       data = UKfiveplus)

# Random Intercept & Fixed Effects model
clmm_happy1 <- clmm(happy ~ ragec + rgndr + domicil + region + intagec + intgndr + (1 | intid),
       weights = pspwght,
       Hess = TRUE,
       na.action = "na.omit",
       data = UKfiveplus)

# Random Intercept & Fixed Effects model with interaction effect
clmm_happy2 <- clmm(happy ~ ragec + rgndr + domicil*region + intagec + intgndr + (1 | intid),
       weights = pspwght,
       Hess = TRUE,
       na.action = "na.omit",
       data = UKfiveplus); 


summary(noint_happy1) # fixed effect only model
summary(clmm_happy1) # random intercept model
summary(clmm_happy2) # random intercept model with interaction

anova(noint_happy1,clmm_happy1) # test RI against no RI
anova(clmm_happy1,clmm_happy2) # test RI w/o Interaction against RI w/ interaction

BIC(noint_happy1); BIC(clmm_happy1); BIC(clmm_happy2)  # check BIC of RI model to FE model

# The ranef function extracts the conditional modes of the random effects from a clmm object. 
# ranef(clmm_happy1)

# Plot EBLUPS
# qqnorm(ranef(clmm_happy1)$intid[,1])
# qqline(ranef(clmm_happy1)$intid[,1])

# Sort and plot interviewer effects with 95% CI
ci1 <- clmm_happy1$ranef + qnorm(0.975) * sqrt(clmm_happy1$condVar) %o% c(-1, 1)
ord.re1 <- order(clmm_happy1$ranef)
ci1 <- ci1[order(clmm_happy1$ranef),]

colors1<-ifelse(ci1[,2]<0, "Red", ifelse(ci1[,1]>0, "Red", "Black"))

plot(clmm_happy1$ranef[ord.re1], axes=FALSE, ylim=range(ci1),
     main = "EBLUP of Interviewer Effect with 95% CI \nTaking all things together, how happy would you say you are?",
     xlab="Interviewer ID (ordered by effect size)", 
     ylab="Interviewer Effect",
     col = colors1); axis(1, at=1:158, labels = ord.re1); axis(2); for(i in 1:158) segments(i, ci1[i,1], i, ci1[i, 2], col = colors1[i]); abline(h = 0, lty=2)
```


# FREEHMS
## freehms1 ~ ragec + as.factor(rgndr) + as.factor(domicil) + as.factor(region) + intagec + intgndr + (1 | intid)
```{r freehms1}
# Fixed Effects only model to test against random intercept model
noint_freehms1 <- clm(freehms ~ ragec + rgndr + domicil + region + intagec + intgndr,
       weights = pspwght,
       Hess = TRUE,
       na.action = "na.omit",
       data = UKfiveplus)

# Random Intercept & Fixed Effects model
clmm_freehms1 <- clmm(freehms ~ ragec + rgndr + domicil + region + intagec + intgndr + (1 | intid),
       weights = pspwght,
       Hess = TRUE,
       na.action = "na.omit",
       data = UKfiveplus)

# Random Intercept & Fixed Effects model with interaction effect
clmm_freehms2 <- clmm(freehms ~ ragec + rgndr + domicil*region + intagec + intgndr + (1 | intid),
       weights = pspwght,
       Hess = TRUE,
       na.action = "na.omit",
       data = UKfiveplus); 


summary(noint_freehms1) # fixed effect only model
summary(clmm_freehms1) # random intercept model
summary(clmm_freehms2) # random intercept model with interaction

anova(noint_freehms1,clmm_freehms1) # test RI against no RI
anova(clmm_freehms1,clmm_freehms2) # test RI w/o Interaction against RI w/ interaction

BIC(noint_freehms1); BIC(clmm_freehms1); BIC(clmm_freehms2)  # check BIC of RI model to FE model

# The ranef function extracts the conditional modes of the random effects from a clmm object. 
# ranef(clmm_freehms1)

# Plot EBLUPS
# qqnorm(ranef(clmm_freehms1)$intid[,1])
# qqline(ranef(clmm_freehms1)$intid[,1])

# Sort and plot interviewer effects with 95% CI
ci2 <- clmm_freehms1$ranef + qnorm(0.975) * sqrt(clmm_freehms1$condVar) %o% c(-1, 1)
ord.re2 <- order(clmm_freehms1$ranef)
ci2 <- ci2[order(clmm_freehms1$ranef),]

colors2<-ifelse(ci2[,2]<0, "Red", ifelse(ci2[,1]>0, "Red", "Black"))

plot(clmm_freehms1$ranef[ord.re2], axes=FALSE, ylim=range(ci2),
     main = "EBLUP of Interviewer Effect with 95% CI \nGay men and lesbians should be free \nto live their own life as they wish. \nTo what extent do you agree?",
     xlab="Interviewer ID (ordered by effect size)", 
     ylab="Interviewer Effect",
     col = colors2); axis(1, at=1:158, labels = ord.re2); axis(2); for(i in 1:158) segments(i, ci2[i,1], i, ci2[i, 2], col = colors2[i]); abline(h = 0, lty=2)
```

# TVTOT
## tvtot1 ~ ragec + as.factor(rgndr) + as.factor(domicil) + as.factor(region) + intagec + intgndr + (1 | intid)
```{r}
# Fixed Effects only model to test against random intercept model
noint_tvtot1 <- clm(tvtot ~ ragec + rgndr + domicil + region + intagec + intgndr,
       weights = pspwght,
       Hess = TRUE,
       na.action = "na.omit",
       data = UKfiveplus)

# Random Intercept & Fixed Effects model
clmm_tvtot1 <- clmm(tvtot ~ ragec + rgndr + domicil + region + intagec + intgndr + (1 | intid),
       weights = pspwght,
       Hess = TRUE,
       na.action = "na.omit",
       data = UKfiveplus)

# Random Intercept & Fixed Effects model with interaction effect
clmm_tvtot2 <- clmm(tvtot ~ ragec + rgndr + domicil*region + intagec + intgndr + (1 | intid),
       weights = pspwght,
       Hess = TRUE,
       na.action = "na.omit",
       data = UKfiveplus); 


summary(noint_tvtot1) # fixed effect only model
summary(clmm_tvtot1) # random intercept model
summary(clmm_tvtot2) # random intercept model with interaction

anova(noint_tvtot1,clmm_tvtot1) # test RI against no RI
anova(clmm_tvtot1,clmm_tvtot2) # test RI w/o Interaction against RI w/ interaction

BIC(noint_tvtot1); BIC(clmm_tvtot1); BIC(clmm_tvtot2)  # check BIC of RI model to FE model

# The ranef function extracts the conditional modes of the random effects from a clmm object. 
# ranef(clmm_tvtot1)

# Plot EBLUPS
# qqnorm(ranef(clmm_tvtot1)$intid[,1])
# qqline(ranef(clmm_tvtot1)$intid[,1])

# Sort and plot interviewer effects with 95% CI
ci3 <- clmm_tvtot1$ranef + qnorm(0.975) * sqrt(clmm_tvtot1$condVar) %o% c(-1, 1)
ord.re3 <- order(clmm_tvtot1$ranef)
ci3 <- ci3[order(clmm_tvtot1$ranef),]

colors3<-ifelse(ci3[,2]<0, "Red", ifelse(ci3[,1]>0, "Red", "Black"))

plot(clmm_tvtot1$ranef[ord.re3], axes=FALSE, ylim=range(ci3),
     main = "EBLUP of Interviewer Effect with 95% CI \nHow much time do you spend watching television?",
     xlab="Interviewer ID (ordered by effect size)", 
     ylab="Interviewer Effect",
     col = colors3); axis(1, at=1:158, labels = ord.re3); axis(2); for(i in 1:158) segments(i, ci3[i,1], i, ci3[i, 2], col = colors3[i]); abline(h = 0, lty=2)
```

# PRAY
## pray1 ~ ragec + as.factor(rgndr) + as.factor(domicil) + as.factor(region) + intagec + intgndr + (1 | intid)
```{r pray1}
# Fixed Effects only model to test against random intercept model
noint_pray1 <- clm(pray ~ ragec + rgndr + domicil + region + intagec + intgndr,
       weights = pspwght,
       Hess = TRUE,
       na.action = "na.omit",
       data = UKfiveplus)

# Random Intercept & Fixed Effects model
clmm_pray1 <- clmm(pray ~ ragec + rgndr + domicil + region + intagec + intgndr + (1 | intid),
       weights = pspwght,
       Hess = TRUE,
       na.action = "na.omit",
       data = UKfiveplus)

# Random Intercept & Fixed Effects model with interaction effect
clmm_pray2 <- clmm(pray ~ ragec + rgndr + domicil*region + intagec + intgndr + (1 | intid),
       weights = pspwght,
       Hess = TRUE,
       na.action = "na.omit",
       data = UKfiveplus); 


summary(noint_pray1) # fixed effect only model
summary(clmm_pray1) # random intercept model
summary(clmm_pray2) # random intercept model with interaction

anova(noint_pray1,clmm_pray1) # test RI against no RI
anova(clmm_pray1,clmm_pray2) # test RI w/o Interaction against RI w/ interaction

BIC(noint_pray1); BIC(clmm_pray1); BIC(clmm_pray2)  # check BIC of RI model to FE model

# The ranef function extracts the conditional modes of the random effects from a clmm object. 
# ranef(clmm_pray1)

# Plot EBLUPS
# qqnorm(ranef(clmm_pray1)$intid[,1])
# qqline(ranef(clmm_pray1)$intid[,1])

# Sort and plot interviewer effects with 95% CI
ci4 <- clmm_pray1$ranef + qnorm(0.975) * sqrt(clmm_pray1$condVar) %o% c(-1, 1)
ord.re4 <- order(clmm_pray1$ranef)
ci4 <- ci4[order(clmm_pray1$ranef),]

colors4<-ifelse(ci4[,2]<0, "Red", ifelse(ci4[,1]>0, "Red", "Black"))

plot(clmm_pray1$ranef[ord.re4], axes=FALSE, ylim=range(ci4),
     main = "EBLUP of Interviewer Effect with 95% CI \nHow often do you pray?",
     xlab="Interviewer ID (ordered by effect size)", 
     ylab="Interviewer Effect",
     col = colors4); axis(1, at=1:158, labels = ord.re4); axis(2); for(i in 1:158) segments(i, ci4[i,1], i, ci4[i, 2], col = colors4[i]); abline(h = 0, lty=2)
```

# ICC Calculations
```{r}
ICC_df<-data.frame(IntVariance = c(0.3409, 0.4062, 0.3266, 0.2575), ResidVariance = c(3.289869,3.289869,3.289869,3.289869))
ICC_df$ICC<-ICC_df$IntVariance/(ICC_df$IntVariance+ICC_df$ResidVariance)
ICC_df$ICC
```